### 2025-08-05 index.qmd
Updated the analysis and the manuscript and the data

Data comes from this Scopus with the specific syntax: `SRCTITLE ( JOURNAL NAME ) AND PUBYEAR > 1999`. We focussed on 5 highest ranked journals in Music Psychology, namely _Musicae Scientiae_, _Psychology of Music_, _Music Perception_, _Journal of New Music Research_, and _Music & Science_. To attribute the gender for the authors, we used genderize API from the extracted first names. We manually checked a subset of the data and attributed some of those names that the API could not resolve.

@@

Data analysis is covered in [analysis.qmd](analysis.qmd) document.

@@

The study report is available [manuscript/manuscript.qmd](manuscript/manuscript.qmd) document.

>>>>

Data comes from this Scopus with the specific syntax: `SRCTITLE ( JOURNAL NAME ) AND PUBYEAR > 1999`. We focussed on 5 journals in Music Psychology, namely _Musicae Scientiae_, _Psychology of Music_, _Music Perception_, _Journal of New Music Research_, and _Music & Science_. To attribute the gender for the authors, we used [genderize API](https://genderize.io/). The details of the process are given in the manuscript.

@@

Data analysis steps are covered in the [analysis.qmd](analysis.qmd) document.

@@

The study report is available at [manuscript/manuscript.qmd](manuscript/manuscript.qmd) document.
